To be FAIR: Theory Specification Needs an Update

### 2025-02-26 dk_example/example.tex
add to dk aexample
finalize DK example draft

% load packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{mathtools}
\usepackage{bbm}

@@

\section{Relationships}

@@

\begin{figure}[ht]
  \vspace{1cm}
  \begin{center}
  \input{figures/original_dk.tex}
  \end{center}
  %\caption{Subtypes of `AbstractSem`.}
  \label{fig:typetree}
\end{figure}

With $-$ signifying a negative association and $\simeq$ signifying measured by.

@@

@@

\noindent From eq. \ref{oc} and \ref{ep} it follows that $p_e = s^*_s$ and further from eq. \ref{ep} and \ref{p} we see
\begin{align}
  oe &= p_e - p \\
  &= (s^* + oc^*) - (s^* + \epsilon) \\
  &= oc^* - \epsilon
\end{align}
\section{(Statistical) Models}

\subsection{Correction}
There are different ways to correct for the bias introduced by measurement error:
\begin{itemize}
 \item use different test performances to calculate skill and overconfidence, but a small test-retest correlation can bias the estimate towards zero then (Krueger and Mueller, 2002)
\end{itemize}

@@

\section{Open Questions / Ambiguities}

>>>>

% load packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{mathtools}
\usepackage{bbm}
\usepackage{float}

@@

\section{Relationships between constructs}

@@

\begin{figure}[H]
  \vspace{1cm}
  \begin{center}
  \input{figures/original_dk.tex}
  \end{center}
  %\caption{Subtypes of `AbstractSem`.}
  \label{fig:typetree}
\end{figure}

With $-$ signifying a negative association and $\simeq$ signifying ``measured by''.

@@

\subsection{Formulation using measurement error}

\begin{figure}[H]
  \vspace{1cm}
  \begin{center}
  \input{figures/error_dk.tex}
  \end{center}
  \caption{A caption}
  \label{fig:typetree}
\end{figure}

With $-$ signifying a negative association, $\simeq$ signifying ``measured by'' and $\coloneq$ signifying ``defined as''.

@@

\noindent From eq. \ref{oc} and \ref{ep} it follows that $p_e = s^*_s$ and further from eq. \ref{ep} and \ref{p} we see
\begin{align} \label{dd}
  oe &= p_e - p \\
  &= (s^* + oc^*) - (s^* + \epsilon) \\
  &= oc^* - \epsilon
\end{align}

\section{(Statistical) Models}
Using a linear regression model, the Dunning-Kruger effect can be stated as
\begin{equation}
 oc^* = \alpha + \beta_1 s^* + u
\end{equation}
with $\beta_1 < 0$.
Substituting the obervable variables and rearranging according to eq. \ref{p} and \ref{dd}:
\begin{equation}
  oe = \alpha + \beta_1 p + u - \epsilon(1 + \beta_1)
\end{equation}

\subsection{Correction}
There are different ways to correct for the bias introduced by measurement error:
\begin{itemize}
 \item Bias correction: use a bias correction formula that takes into account the correlation between performance and the error term
 \item IV approach: measure performance on a second test ($p_2$) and compute $\beta_1 = \frac{\cov(oe, p_2)}{\cov(p, p_2)}$.
\end{itemize}

@@

\section{Open Questions / Ambiguities}
The paper states they assume performance expectations are measured before the test - the derivations differ substantially if they are measured after the test.

### 2025-02-26 dk_example/figures/error_dk.tex
finalize DK example draft

%arrows
\draw[-,>=stealth',semithick] (skill) -- node [fill=white] {$-$} (overconfidence);
\draw[-,>=stealth',semithick] (performance) -- node [fill=white] {$-$} (estimate);
\draw[-,>=stealth',semithick] (skill) -- node [fill=white] {$\simeq$} (performance);
\draw[-,>=stealth',semithick] (overconfidence) -- node [fill=white] {$\simeq$} (estimate);

>>>>

\node[manifest] at (0, -6) (skillerror) {\texttt{skill + error}};

\node[manifest] at (6, -4) (pminusp) {\texttt{expected performance - performance}};

\node[manifest] at (6, -6) (ocerror) {\texttt{overconfidence - error}};

%arrows
\draw[-,>=stealth',semithick] (skill) -- node [fill=white] {$-$} (overconfidence);
\draw[-,>=stealth',semithick] (performance) -- node [fill=white] {$-$} (estimate);
\draw[-,>=stealth',semithick] (skill) -- node [fill=white] {$\simeq$} (performance);
\draw[-,>=stealth',semithick] (overconfidence) -- node [fill=white] {$\simeq$} (estimate);
\draw[-,>=stealth',semithick] (skillerror) -- node [fill=white] {$-$} (ocerror);
\draw[-,>=stealth',semithick] (performance) -- node [fill=white] {$\coloneq$} (skillerror);
\draw[-,>=stealth',semithick] (estimate) -- node [fill=white] {$\coloneq$} (pminusp);
\draw[-,>=stealth',semithick] (pminusp) -- node [fill=white] {$=$ (derived below)} (ocerror);
